### 2022-03-31 README.Rmd
c4a_citation added

* `c4a_palettes` Get available palette names
* `c4a_series` Get available series
* `c4a_meta` Get meta information (such as type and maximum number of colors )
* `c4a_ls` Environment via which palette names can be browsed with auto-completion (using `$`)

>>>>

* `c4a_palettes` Get available palette names
* `c4a_series` Get available series names
* `c4a_info` Get palette information (such as type and maximum number of colors)
* `c4a_citation` Show how to cite palettes (with bibtex code).
* `.P` Environment via which palette names can be browsed with auto-completion (using `$`)
